Decompositions of congruence subgroups of Chevalley groups

### 2015-10-09 paper.tex
Tiny fixes

Applying \cref{thm:DennisVaserstein} and generalizing Nikolov's \cite[Proposition~1]{NikProdDecomp} in the special case $\Phi=\rD_\ell$ to arbitrary rings we obtain the following result.
\begin{thm}\label{thm:spin-sln-prod}
Assume that $\sr(I) \leqslant 2$. Then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of its (regularly embedded) subgroups of type $\rA_{\ell-1}$.
\end{thm}

>>>>

Applying \cref{thm:DennisVaserstein} and proving a more accurate version of \cite[Proposition~1]{NikProdDecomp} in the special case $\Phi=\rD_\ell$ we obtain the following result.
\begin{thm}\label{thm:spin-sln-prod}
Assume that $\sr(I) \leqslant 2$. Then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of its (regularly embedded) subgroups of type $\rA_{\ell-1}$.
\end{thm}
